Text as Policy: Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2016-01-20 manuscript/text_reuse.tex
updated title
a little descriptive plot

\title{Identifying Equivalent State Bills through Text Reuse. \large Subtitle.}
\date{\today}
\author{Bruce Desmarais, Matt Burgess, Fridolin Linder, Eugenia Giraudi}

@@

>>>>

\title{Text as Policy: Identifying Equivalent State Bills through Text Reuse. \large Subtitle.}
\date{\today}
\author{Bruce Desmarais, Matt Burgess, Fridolin Linder, Eugenia Giraudi}

@@

Figure \ref{fig:bill_desc} displays the year ranges and number of bills in the bill data base.

\begin{figure}[]
    \centering
    \includegraphics{figures/year_count_by_state.png}
    \caption{Description of the bill database. The horizontal bars display the time range for which bills are available for each state. The color of the bar indicates how many bills are available for this state.}
    \label{fig:bill_desc}
\end{figure}<++>
